Algebraic File Synchronization: Adequacy and Completeness

### 2017-10-28 p2/upd-correct.tex
We don't need the canonical mapping
Fix: simplifying the sequence may increase the domain

@@

We therefore know that $S_1\indep\ucx$ and so
from \cref{ax_separate_commute}
\[ S \equiv S_0\cc\ucy\cc\ucx\cc S_1 \cc S_2. \]
We can apply \cref{ax_same_emptyseq,ax_same_singlec} to
$\ucy\cc\ucx$ and get a $S'\equiv S$ that contains one or two less commands on $n$.
Repeating the swap and the simplification we
can convert $S$ into an equivalent simple sequence.
Let this sequence be $S^*$.

>>>>

TODO What is not trivial here is that $U$ works at all.

@@

We therefore know that $S_1\indep\ucx$ and so
from \cref{ax_separate_commute}
\[ S \equiv S_0\cc\ucy\cc\ucx\cc S_1 \cc S_2. \]
We can apply \cref{ax_same_emptyseq,ax_same_singlec} to
$\ucy\cc\ucx$ and get a $S'\eqext S$ that contains one or two less commands on $n$.
Repeating the swap and the simplification we
can convert $S$ into an equivalent simple sequence.
Let this sequence be $S^*$.
